---
title: "workshop_R3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read survey csv that have problem data
```{r}
survey.program1 = read.csv("survey_messy.csv", header = TRUE)
print(survey.program1)
```


```{r}
tv.hours.messey <- survey.program1$TVhours
as.character(tv.hours.messey)[1:30]
```


ทำข้อมูลให้สะอาด ค่าไหนที่ควรเป็นตัวเลข ต่กรอกมาไม่ถูก ก็จะให้เป็น NA ซึ่งทางสถิติ จะไม่ให้ใส่ค่า 0
```{r}
as.numeric(as.character(tv.hours.messey))[1:30]
```

```{r}
typeof(as.numeric(as.character(tv.hours.messey)))
```

```{r}
tv.hours.strings <- as.character(tv.hours.messey)
tv.hours.strings
```

แทนที่ตัวอักษรที่ไม่ต้องการออกไปด้วยค่าว่าง
```{r}
gsub("[^0-9]", "", tv.hours.strings)
```

```{r}
tv.hours.clean <- as.numeric(gsub("[^0-9]", "", tv.hours.strings))
tv.hours.clean
```


Transform, replace column value with cleaned data 
```{r}
survey <- transform(survey.program1, TVhours = as.numeric(gsub("[^0-9]", "", TVhours)))
str(survey)
```

```{r}
qplot(x = EngineSize, y = Price, data = Cars93)
```

```{r}
ggplot(Cars93, aes(x=EngineSize, y=Price)) + geom_point()
```

With color, shape
```{r}
ggplot(Cars93, aes(x=EngineSize, y=Price, color = Type, shape = DriveTrain)) + geom_point()
```


```{r}
ggplot(Cars93, aes(x=EngineSize, y=Price, color = Type,label = DriveTrain)) + geom_label()
```


เปลี่ยนชื่อ columns
```{r}
colnames(birthwt)

colnames(birthwt) <- c("birthwt.below.2500", "mother.age", "mother.weight", "race", "mother.smokes", "previous.prem.labor", "hypertension", "uterine.irr", "physician.visits", "birthwt.grams")

colnames(birthwt)

```

จัดข้อมูลให้สวยงาม
```{r}
birthwt <- transform(birthwt, 
  race = as.factor(mapvalues(race, c(1,2,3), c("white", "black", "other"))), 
  mother.smokes = as.factor(mapvalues(mother.smokes, c(0,1), c("no", "yes"))), 
  hypertension = as.factor(mapvalues(hypertension, c(0, 1), c("no", "yes"))), 
  uterine.irr = as.factor(mapvalues(uterine.irr, c(0, 1), c("no", "yes"))), 
  birthwt.below.2500 = as.factor(mapvalues(birthwt.below.2500, c(0, 1), c("no", "yes"))))
  
```


```{r}
sleepData <- select(msleep, -name, -sleep_total)
print(sleepData)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
